
---
title: "Study Hours vs Final Score"
author: "SB"
format:
  html:
    toc: true
    number-sections: true
execute:
  echo: true
  message: false
  warning: false
---

# Overview

This report summarizes the relationship between study hours and final exam scores using processed project data.

The analysis includes:

- Basic summary statistics  
- A linear regression model  
- A visualization of the relationship  

---

# Load Required Libraries

```{r}
library(readr)
library(dplyr)
library(ggplot2)
```

---

# Load Processed Data

```{r}
scores <- read_csv("../data/processed/scores_clean.csv", show_col_types = FALSE)
head(scores)
```

---

# Summary Statistics

```{r}
summary_stats <- scores |>
  summarise(
    total_observations = n(),
    avg_study_hours = mean(study_hours),
    avg_final_score = mean(final_score),
    min_final_score = min(final_score),
    max_final_score = max(final_score)
  )

summary_stats
```

---

# Linear Regression Model

```{r}
model <- lm(final_score ~ study_hours, data = scores)
summary(model)
```

---

# Visualization

```{r}
ggplot(scores, aes(x = study_hours, y = final_score)) +
  geom_point(color = "blue") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(
    title = "Final Score vs Study Hours",
    x = "Study Hours",
    y = "Final Score"
  ) +
  theme_minimal()
```

---

# Conclusion

This example demonstrates:

- How to separate data processing from reporting  
- How to generate reproducible reports with Quarto  
- How to maintain a clean project structure  

By keeping data, reusable functions, scripts, and reports organized, your workflow becomes easier to scale and reproduce.
